Analysis of Odd one out experiment

### 2020-05-20 reports/DRM_exp/analysis_DRM_after_review.Rmd
changes for review

@@

## Divide distractors by distance to targets - mean

```{r}
divide_into_groups_tgt_dist_mean <- function(dfxx) {

  rnk <- rank(dfxx_notgt$mean_tgt_dist)

df2_tgt <- df2_tgt %>% ungroup() %>% distinct()
df2_tgt_modeldist_mean <- df2_tgt %>% 
  filter(layer == "dist_to_tgts") %>% 
  group_by(subject_id,grp_order) %>% 
  do(divide_into_groups_tgt_dist_mean(.))

df2_tgt_modeldist_mean %>% xtabs(~type+model_type,.) %>% prop.table(1)
df2_tgt_modeldist_mean %>% filter(type!="target") %>% xtabs(~type+model_type,.) %>% psych::phi()
df2_tgt_modeldist_mean %>% filter(type != "target") %>% 
  group_by(model_type) %>% 
  summarize(correct = mean(correct))

df2_tgt_modeldist_mean %>% filter(type != "target") %>% 
  group_by(type) %>% 
  summarize(correct = mean(correct))

@@

glmm_orig_model <- df_models_res %>% glmer(correct~category_centroid_type+(1+category_centroid_type|subject_id) + (1|category), ., family = binomial())
glmm_dist_to_tgt <- df_models_res %>% glmer(correct~min_dist_to_tgt + (1+min_dist_to_tgt|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv5 <- df_models_res %>% glmer(correct~dist_to_proto5 + (1+dist_to_proto5|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv3 <- df_models_res %>% glmer(correct~dist_to_proto3 + (1+dist_to_proto3|subject_id) + (1|category),., family = binomial())
glmm_memorability <- df_models_res %>% glmer(correct~memorability_model + (1+memorability_model|subject_id) + (1|category),., family = binomial())
models_list <- list(glmm_null_model,glmm_orig_model,glmm_dist_to_tgt,glmm_dist_to_proto_conv5,glmm_dist_to_proto_conv3,glmm_memorability)
models_list %>% 
  map(performance::r2_nakagawa) %>%
  map_dbl("R2_conditional") %>% 
  round(2)

@@

```{r}
cont_entropy <- read_csv(here("data/exp_DRM1/cats_entrophy.csv"), col_names = F) %>% rename(category = X1, cont_entropy = X2) %>% mutate(category = str_replace(category, "_", " "))
df_cont_entropy <- df %>% left_join(cont_entropy, by = "category") 
df_cont_entropy %>% 
  ggplot(aes(x = category, y = correct, col = type, group = type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line")

@@

df_cont_entropy %>% 
  filter(type == "close distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()  + 
  ggtitle("Close distractors")

df_cont_entropy %>% 
  filter(type == "far distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel() + 
  ggtitle("Far distractors")

@@

>>>>

## Means and SD for confidence

```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
df %>% 
  mutate(confidence_n = factor(confidence, levels = c("not at all sure","somewhat sure","very sure"))) %>% 
  group_by(type) %>% 
  summarise(modus = Mode(confidence),
            mean = mean(as.numeric(confidence_n)),
            sd = sd(as.numeric(confidence_n)),
            median = median(as.numeric(confidence_n)))
```

@@

@@

glmm_orig_model <- df_models_res %>% glmer(correct~category_centroid_type+(1+category_centroid_type|subject_id) + (1|category), ., family = binomial())
glmm_dist_to_tgt <- df_models_res %>% glmer(correct~min_dist_to_tgt + (1+min_dist_to_tgt|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv5 <- df_models_res %>% glmer(correct~dist_to_proto5 + (1+dist_to_proto5|subject_id) + (1|category),., family = binomial())
glmm_dist_to_proto_conv3 <- df_models_res %>% glmer(correct~dist_to_proto3 + (1+dist_to_proto3|subject_id) + (1|category),., family = binomial())
glmm_memorability <- df_models_res %>% glmer(correct~memorability_model + (1+memorability_model|subject_id) + (1|category),., family = binomial())
models_list <- list(glmm_null_model,glmm_orig_model,glmm_dist_to_tgt,glmm_dist_to_proto_conv3,glmm_dist_to_proto_conv5,glmm_memorability)
models_list %>% 
  map(performance::r2_nakagawa) %>%
  map_dbl("R2_conditional") %>% 
  round(2)

@@

```{r}
cont_entropy <- read_csv(here("data/exp_DRM1/cats_entrophy.csv"), col_names = F) %>% rename(category = X1, cont_entropy = X2) %>% mutate(category = str_replace(category, "_", " "))
df_cont_entropy <- df %>% left_join(cont_entropy, by = "category") 
p <- df_cont_entropy %>% 
  mutate(FA = 1 - correct) %>% 
  filter(type != "target") %>% 
  ggplot(aes(x = category, y = FA, col = type, group = type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun = "mean", geom = "line") +

  scale_x_discrete(guide = guide_axis(n.dodge=3))

ggsave(file.path(plots_dir, "Figurexx_categories_FA.svg"), p, width = 12, height = 6)

@@

p <- df_cont_entropy %>% 
  filter(type == "close distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = cont_entropy, y = FA, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()  + 
  ggtitle("Close distractors") +
  ylab("FA") + 
  xlab("context entropy") +
  stat_smooth(method = "lm")
p
df_cont_entropy %>% 
  filter(type == "close distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  cor.test(~FA+cont_entropy,., method = "sp")

df_cont_entropy %>% 
  filter(type == "far distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  cor.test(~FA+cont_entropy,., method = "sp")

ggsave(file.path(plots_dir, "Figurexx_categories_close_dist_CE.svg"), p, width = 6, height = 6)
df_cont_entropy %>% 
  filter(type == "far distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct), cont_entropy = mean(cont_entropy)) %>% 
  ggplot(aes(x = FA, y = cont_entropy, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel() + 
  ggtitle("Far distractors")

@@

## FAbility

```{r}
df_dist <- df %>% filter(type != "target") %>% group_by(type, img_name) %>% 
  summarize(FA = mean(1-correct), dist_to_cat_center_fc7 = mean(dist_to_cat_center_fc7), dist_to_proto_conv3 = mean(dist_to_proto_conv3), dist_to_proto_conv5 = mean(dist_to_proto_conv5)) %>% ungroup()
df_dist %>% select(-type,-img_name) %>% 
  as.matrix() %>% 
  Hmisc::rcorr(type = "spearman")

df_dist %>% ggplot(aes(x = dist_to_proto_conv3, y = FA, col =type)) + geom_point() + stat_smooth( method = "lm")

df_dist %>% select(-type,-img_name) %>% 
  as.matrix() %>% 
  Hmisc::rcorr()
df_dist %>% ggplot(aes(x = dist_to_proto_conv5, y = FA, col =type)) + geom_point() + stat_smooth( method = "lm")

df2_tgt_corr <- df2_tgt %>% distinct() %>% filter(type != "target") %>% group_by(layer, type, img_name) %>% 
  summarize(FA = mean(1-correct), dist_to_tgt = mean(min_tgt_dist_no0)) %>% ungroup()

df2_tgt_corr %>% filter(layer == "dist_to_tgts") %>% 
  select(-type,-img_name,-layer) %>% 
  as.matrix() %>% 
  Hmisc::rcorr(type = "sp")

df2_tgt_corr %>% filter(layer == "dist_to_tgts_conv3") %>% 
  select(-grp_order,-layer) %>% 
  group_by(type) %>% 
  do(cor.test(~FA+dist_to_tgt,.) %>% broom::tidy())
  as.matrix() %>% 
  Hmisc::rcorr(type = "sp")

dfm %>%  filter(type != "target") %>% group_by(type, img_name) %>% 
  summarize(FA = mean(1-correct), mem_score = mean(mem_score))  %>% 
  ggplot(aes(x = mem_score, y = FA, col =type)) + geom_point() + stat_smooth( method = "lm")

dfm %>% filter(type != "target") %>% group_by(type, img_name) %>%
    summarize(FA = mean(1-correct), mem_score = mean(mem_score))  %>% 
  cor.test(~FA+mem_score,.)

## Hits and FAs

```{r}
df_hits <- df %>% 
    filter(type == "target") %>% 
  group_by(category) %>% 
  summarize(H = mean(correct))

df_fas <- df %>% 
    filter(type == "close distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct))
df_hits %>% left_join(df_fas) %>% ggplot(aes(x = H, y = FA, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()
df_hits %>% left_join(df_fas) %>% cor.test(~H+FA,., method = "sp")

df_hits %>% left_join(df_fas) %>% filter(category!="badlands") %>% ggplot(aes(x = H, y = FA, label = category)) +
  geom_point()+
  ggrepel::geom_label_repel()

df_hits <- df %>% 
    filter(type == "target") %>% 
  group_by(category) %>% 
  summarize(H = mean(correct))

df_fas_far <- df %>% 
    filter(type == "far distractor") %>% 
  group_by(category) %>% 
  summarize(FA = mean(1-correct))

df_hFA_close <- df_hits %>% left_join(df_fas)
df_hFA_far <- df_hits %>% left_join(df_fas_far)

df_hFA_close %>% filter(category!="badlands") %>% cor.test(~H+FA,.,method ="sp")
df_hFA_close %>% cor.test(~H+FA,.,method ="sp")
df_hFA_far %>% cor.test(~H+FA,.,method ="sp")
```

## FAbility - with category corrections

```{r}
df

### 2020-05-20 reports/DRM_exp/analysis_DRM_exp1.Rmd
changes for review

p <- df %>%
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = .5) +
  ylab("Perc. correct") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))

>>>>

p <- df %>%
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct)) %>% 
  ggplot(aes(x = type, y = correct)) + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = .5) +
  ylab("Percentage correct") +
  geom_violin(trim = F)+
  stat_summary(fun.data = "mean_cl_boot") + 
  xlab("Type") +
  theme(text = element_text(size = 24))

### 2020-05-20 reports/odd_one_out/analysis_oddoneout.Rmd
changes for review

p <- metrics2 %>% 
  filter(metric!= "correct", metric != "metrics_combined_correct", metric != "metrics_max_correct") %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_cartesian(ylim = c(0,0.5)) +
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_discrete("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT","upper bound"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3","black")) + # humans - "#FF7F00",
  stat_summary(fun.y=mean, geom="line") +
  theme(text = element_text(size=18))+
  ggtitle("Predict human performance")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman.svg"), p, width = 6, height = 6)
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman_noleg.svg"), p+theme(legend.position="none"), width = 6, height = 6)

p <- metrics %>% 
  ggplot(aes(x = quintile, y = value_partic_top3, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_cartesian(ylim = c(0,0.5)) +
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/3) +
  ylab("Perc. correct") +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3")) + 
  stat_summary(fun.y=mean, geom="line") +
  theme(text = element_text(size=18))+
  ggtitle("Predict human performance")
  #theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman_top3.svg"), p, width = 6, height = 6)
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman_top3_noleg.svg"), p+theme(legend.position="none"), width = 6, height = 6)

>>>>

p <- metrics2 %>% 
  filter(metric!= "correct", metric != "metrics_combined_correct", metric != "metrics_max_correct") %>% 
  ggplot(aes(x = quintile, y = value_partic, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_cartesian(ylim = c(0,0.5)) +
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  scale_x_discrete("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT","upper bound"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3","black")) + # humans - "#FF7F00",
  stat_summary(fun=mean, geom="line") +
  theme(text = element_text(size=18))+
  ggtitle("Predict human performance")
#theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman.svg"), p, width = 6, height = 6)
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman_noleg.svg"), p+theme(legend.position="none"), width = 6, height = 6)

p <- metrics %>% 
  ggplot(aes(x = as.character(quintile), y = value_partic_top3, col = metric, group = metric)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  coord_cartesian(ylim = c(0,0.5)) +
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/3) +
  ylab("Perc. correct") +
  scale_x_discrete("Quintile", breaks = c(2,3,4), labels = c("2","3","4")) +
  scale_color_manual(labels = c("GIST", "HOG", "RGB", "SIFT"), values = c("#E41A1C","#377EB8","#4DAF4A","#984EA3")) + 
  stat_summary(fun=mean, geom="line") +
  theme(text = element_text(size=18))+
  ggtitle("Predict human performance")
#theme(legend.justification = c(1,1), legend.position=c(0.99,0.99))
p
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman_top3.svg"), p, width = 6, height = 6)
ggsave(file.path(plots_dir, "Fig_chp3_metrics_predicthuman_top3_noleg.svg"), p+theme(legend.position="none"), width = 6, height = 6)
